\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\title{DNS Testing Procedures}
\author{}
\date{}
\maketitle

\section*{DNS Resolution Testing}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Objective:} Ensure the BIND server correctly resolves domain names.
    \item \textbf{Method:} Use the \texttt{dig} command to query the DNS server for known domains. Check \texttt{A}, \texttt{AAAA}, \texttt{MX}, and \texttt{NS} records:
    \begin{verbatim}
    dig @<DNS-server> example.com [A, AAAA, MX, NS]
    \end{verbatim}
    \item \textbf{Expected Outcome:} Each query returns the correct IP addresses and record details.
\end{itemize}

\section*{Forward and Reverse DNS Lookup}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Objective:} Verify that forward and reverse lookups are functional.
    \item \textbf{Method:}
    \begin{itemize}
        \item Use \texttt{dig} for forward lookup (domain to IP):
        \begin{verbatim}
        dig @<DNS-server> example.com A
        \end{verbatim}
        \item Use \texttt{dig -x} for reverse lookup (IP to domain):
        \begin{verbatim}
        dig @<DNS-server> -x [192.0.2.1]
        \end{verbatim}
    \end{itemize}
    \item \textbf{Expected Outcome:} Accurate mapping between domain names and IP addresses.
\end{itemize}

\section*{Zone Transfer Test}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Objective:} Ensure zone transfers between primary and secondary DNS servers are working.
    \item \textbf{Method:} Initiate a zone transfer using \texttt{dig AXFR} and check logs for the transfer:
    \begin{verbatim}
    dig @<primary-DNS-server> example.com AXFR
    \end{verbatim}
    \item \textbf{Expected Outcome:} Zone data is accurately replicated between primary and secondary servers.
\end{itemize}

\section*{DNS Failover Testing}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Objective:} Assess the resilience and reliability of the DNS service under failure conditions.
    \item \textbf{Method:}
    \begin{itemize}
        \item Simulate a failure of the primary DNS server.
        \item Monitor the response from the secondary DNS server:
        \begin{verbatim}
        dig @<secondary-DNS-server> example.com A
        \end{verbatim}
        \item Record any downtime experienced during the transition.
    \end{itemize}
    \item \textbf{Expected Outcome:} The secondary DNS server seamlessly takes over with little to no disruption in DNS resolution.
\end{itemize}

\section*{Stress Testing}
\begin{itemize}[leftmargin=1.5cm]
    \item \textbf{Objective:} Test the performance of the server under high load.
    \item \textbf{Method:} Use tools such as \texttt{dnsperf} to simulate a high number of DNS queries:
    \begin{verbatim}
    dnsperf -s <primary-DNS-IP> -d queries.txt -l 30
    \end{verbatim}
    \item \textbf{Expected Outcome:} The server maintains accuracy and performs well under the load.
\end{itemize}

\end{document}
